### 2020-06-04 notebook/import.Rmd
update imports
support hash validation

```{r birds}
bench_time(
  neon_download("DP1.10003.001", file_regex = ".*basic.*[.]csv")
)
```

```{r beetles}
bench::bench_time(
  neon_download("DP1.10022.001")
)
```

```{r ticks}
bench::bench_time(
  neon_download("DP1.10093.001", quiet = TRUE)
)
```

```{r mammals}
bench::bench_time(
  neon_download("DP1.10072.001",  quiet = TRUE)
)
```

```{r zooplankton}
neon_download("DP1.20219.001")
```

```{r macroinvert}
neon_download("DP1.20120.001")
```

```{r mozzies}
bench::bench_time(
  neon_download("DP1.10043.001")
)
```

# Explore

```{r}
library(dplyr)

meta <- neon_index()
meta %>% count(product)
```

```{r}
meta %>% count(name)
```

```{r}

bench::bench_time({
f <- meta %>% filter(name == "brd_countdata", type == "basic") %>% pull(path)
df <- neon_read(f) # vroom with error handler
})

@@

```{r}

bench::bench_time({
f <- meta %>% filter(name == "mam_perplotnight", type == "basic") %>% pull(path)
df <- neon_read(f) # vroom with error handler
})

```{r}
as_tibble(df)
```

>>>>

# Checksum comparison

The NEON API returns 32 character crc32 checksum

```{r}
raw_files <- neon_index(table = "brd_countdata-expanded")
x <- raw_files$path[[1]]
digest::digest(x, algo = "crc32", file = TRUE)

url <- paste("https://data.neonscience.org/api/v0/data", 
                raw_files$product[[1]], 
                "BART", 
                raw_files$month[[1]], 
                sep = "/")
resp <- httr::GET(url)
out <- jsonlite::fromJSON(httr::content(resp, "text"))$data$files
out[out$name == basename(x),]

dir.create("tmp")
paste0("tmp/", out$name)
purrr::walk2(out$url, paste0("tmp/", out$name), curl::curl_download)
unzip("tmp/NEON.D01.BART.DP1.10003.001.2015-06.expanded.20191107T154457Z.zip",
      exdir = "tmp/expanded")
```

```{r}
vapply(fs::dir_ls("tmp", glob="*.csv"), digest::digest,  character(1L), algo = "crc32", file = TRUE, USE.NAMES = FALSE)
vapply(fs::dir_ls("tmp/expanded", glob="*.csv"), digest::digest, character(1L), algo = "crc32", file = TRUE, USE.NAMES = FALSE)

out$crc32[grepl("[.]csv",out$name)]

@@
